State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed the table of parameters
changed the margin

%<-comment out this for checking equations (author list too)
% \usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
%This is to decrease the space in subfigure command
\usepackage[tight,scriptsize]{subfigure}
\makeatletter
\renewcommand{\subfigtopskip}{1\p@}
\renewcommand{\subfigcapskip}{0\p@}
\renewcommand{\subfigcaptopadj}{1\p@}
\renewcommand{\subfigbottomskip}{1\p@}
\renewcommand{\subfiglabelskip}{0.05em plus 0.02em minus 0.01em}
\makeatother
% \usepackage{pstool}
\renewcommand{\subcapsize}{\small}
 \usepackage{anysize}							%<-use this for checking equation length
 % \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
 %  \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
  \usepackage{amsmath}
\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
\begin{document}

@@

%The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
\section{Results}\label{ResultsSection} The neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. An example of the simulated field can be seen in figure~\ref{fig:experimental design}(a). This figure demonstrates the experimental design used where the sensor array was placed in the centre of the field (sensor centres marked by crosses). This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions. Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f$ characteristics of intracranial EEG.
\begin{table}

@@

	$f_{max}$ & 20 & spikes/s \\

@@

\end{table}

@@

   		\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePy_1.pdf} 

@@

   	\caption{Example of experimental design and model output. \textbf{a}. Example of the neural field with sensors. The centres of the sensors are shown by crosses. \textbf{b} Example of data generated by the model through a subset of the observations. \textbf{c}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} 

@@

\begin{figure*}[th]
\subfigure[]{\includegraphics[scale=0.5]{./Graph/ZetaConvergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta0Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta1Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.5]{./Graph/theta2Convergence.pdf}}

@@

\end{figure*}

>>>>

%<-comment out this for checking equations (author list too)
% \usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
%This is to decrease the space in subfigure command
\usepackage[tight,scriptsize]{subfigure}
\makeatletter
\renewcommand{\subfigtopskip}{1\p@}
\renewcommand{\subfigcapskip}{0\p@}
\renewcommand{\subfigcaptopadj}{1\p@}
\renewcommand{\subfigbottomskip}{1\p@}
\renewcommand{\subfiglabelskip}{0.05em plus 0.02em minus 0.01em}
\makeatother
% \usepackage{pstool}
\renewcommand{\subcapsize}{\small}
 \usepackage{anysize}							%<-use this for checking equation length
  \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
   \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
  \usepackage{amsmath}
\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}}
\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}
\begin{document}

@@

%The method is appropriate for state estimation of stochastic nonlinear dynamical systems. 
\section{Results}\label{ResultsSection} The neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. An example of the simulated field can be seen in figure~\ref{fig:experimental design}(a). This figure demonstrates the experimental design used where the sensor array was placed in the centre of the field (sensor centres marked by crosses). This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions. Figure~\ref{fig:experimental design}(b) shows example data from the sensors of the model, and figure~\ref{fig:experimental design}(c) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f$ characteristics of intracranial EEG.
\begin{table*}

@@

	$f_{max}$ & 10 & spikes/s \\

@@

\end{table*}

@@

   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigureEEGPy.pdf}} \\
   		\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ExperimentFigurePSDPy.pdf}} \\

@@

   	\caption{Example of experimental design and model output.  \textbf{a} Example of data generated by the model through a subset of the observations. \textbf{b}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} 

@@

\subfigure[]{\includegraphics[scale=0.55]{./Graph/ZetaConvergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta0Convergence.pdf}}\\
\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta1Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta2Convergence.pdf}}

@@
